---
title: "Mining China biodiversity from the National Specimen Information Infrastructure"
author: "Liuyong Ding"
date: "3/25/2021"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Mining China biodiversity from the National Specimen Information Infrastructure}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This **rnsii** package programatically download Chinese biodiversity data from the National Specimen Information Infrastructure <http://www.nsii.org.cn> .


## Installation


### Current beta / GitHub release:

Installation using R package
[**devtools**](https://cran.r-project.org/package=devtools):
```{r}
if (!requireNamespace(c("devtools","tibble"), quietly = TRUE))
  install.packages("devtools","tibble")
    
devtools::install_github("Otoliths/rnsii")

```

##  Example

###### Load the **rnsii** package
```{r}
library("rnsii")
```
##### Take "Artemisia argyi"

###### Download specimen data from the NSII

```{r}
result1 <- get_nsii(query = "Artemisia argyi",offset = 0)
```

```{r}
str(result1)
```

```{r}
tibble::tibble(result1$data)
```


###### Download occurrence data from the NSII

```{r}
result2 <- get_occ(query = "Artemisia argyi")
```


```{r}
str(result2)
```

### How to cite this package
```{r}
citation("rnsii")
```


##  Contribution

Contributions to this package are welcome. 
The preferred method of contribution is through a GitHub pull request. 
Feel also free to contact us by creating [**an issue**](https://github.com/Otoliths/rnsii/issues).
